The Argennon Virtual Machine

### 2021-03-22 tex/avm.tex
Add memory spooling
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

% Packages
%\usepackage{amsmath}
%\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\lstset{
%  basicstyle=\ttfamily,
    mathescape
}
%\binoppenalty=99999
%\relpenalty=99999

@@

    \subsection{ZK-EDB Servers}\label{subsec:zk-edb-servers}

@@

    \subsection{Memory Allocation and De-allocation}\label{subsec:memory-allocation-and-de-allocation}

@@

    Every block of the Argennon blockchain contains a list of transactions. This list is an ordered list and the
    effect of its contained transactions must be applied to the AVM state sequentially as they appear in the ordered
    list. This ordering is solely chosen by the block proposer, and users should not have any assumption about
    the ordering of transactions in a block.

@@

@@

    %##\includegraphics[width=17cm]{../img/Alg3s.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{CC}{Counter}
        \SetKwFunction{Inc}{Increment}\SetKwFunction{Dec}{Decrement}\SetKwFunction{AtomInc}{AtomicIncrement}
        \SetKwFunction{AtomDec}{AtomicDecrement}\SetKwFunction{AtomSet}{AtomicSet}
        \SetKwProg{Fn}{Function}{}{}
        \BlankLine
        \Fn{\Inc{\CC, value, seed}}
        {
            $i \gets seed \bmod \CC.size$\;
            \AtomInc{$\CC.cell[i]$, value}\;
        }
        \BlankLine
        \Fn{\Dec{\CC, value, seed, attempt}}
        {
            \If {attempt = \CC.size}
            {
                restore \CC by adding back the subtracted value\;
                \KwRet{Error}\;
            }
            $i \gets seed \bmod \CC.size$\;
            $i \gets (i + attempt) \bmod \CC.size$\;
            \eIf {$\CC.cell[i] \geq value$}
            {
                \AtomDec{$\CC.cell[i]$, value}\;
            }{
                $r \gets value - \CC.cell[i]$\;
                \AtomSet{$\CC.cell[i]$, $0$}\;
                \Dec{\CC, r, seed, $attempt + 1$}\;
            }
        }
        \caption{Concurrent counter}\label{alg:CC}
    \end{algorithm}

>>>>

% Packages
%\usepackage{amsmath}
%\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{cleveref}
\lstset{
%  basicstyle=\ttfamily,
    mathescape
}
%\binoppenalty=99999
%\relpenalty=99999

@@

    \subsection{Incentives for ZK-EDB Servers}\label{subsec:zk-edb-servers}

@@

    \subsection{Memory Allocation and De-allocation Fee}\label{subsec:memory-allocation-and-de-allocation}

@@

    Every block of the Argennon blockchain contains a list of transactions. This list is an ordered list and the
    effect of its contained transactions must be applied to the AVM state sequentially as they appear in the ordered
    list. This ordering is solely chosen by the block proposer, and users should not have any assumptions about
    the ordering of transactions in a block.

@@

    \subsection{Memory Spooling}\label{subsec:spooling}

    When two transactions are dependant and they are connected with an edge \((u,v)\) in the execution DAG,
    the transaction \(u\) needs to be run before the transaction \(v\). However, if \(v\) does not read any
    memory locations that \(u\) modifies, we can run \(u\) and \(v\) in parallel. We just need to make sure
    \(u\) does not see any changes \(v\) is making in AVM memory. This can be done by appropriate versioning
    of the memory locations which is shared between \(u\) and \(v\). We call this method \emph{memory spooling}.
    After enabling memory spooling between two transactions the edge connecting them can be safely removed from the
    execution DAG\@.

@@

    %##\includegraphics[width=17cm]{../img/Alg3s.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{CC}{Counter}
        \SetKwFunction{Inc}{Increment}\SetKwFunction{Dec}{Decrement}\SetKwFunction{AtomInc}{AtomicIncrement}
        \SetKwFunction{AtomDec}{AtomicDecrement}\SetKwFunction{AtomSet}{AtomicSet}\SetKwFunction{Get}{GetValue}
        \SetKwFunction{Acquire}{Lock.Acquire}\SetKwFunction{Release}{Lock.Release}
        \SetKwProg{Fn}{Function}{}{}
        \Fn{\Get{\CC}}
        {
            $s \gets 0$\;
            \Acquire{}\;
            \For{$i \gets 0$ \KwTo $\CC.size - 1$}
            {
                $s \gets s + \CC.cell[i]$\;
            }
            \Release{}\;
            \KwRet{s}\;
        }
        \BlankLine
        \Fn{\Inc{\CC, value, seed}}
        {
            $i \gets seed \bmod \CC.size$\;
            \AtomInc{$\CC.cell[i]$, value}\;
        }
        \BlankLine
        \Fn{\Dec{\CC, value, seed, attempt}}
        {
            \If {attempt = \CC.size}
            {
                restore \CC by adding back the subtracted value\;
                \KwRet{Error}\;
            }
            $i \gets seed \bmod \CC.size$\;
            $i \gets (i + attempt) \bmod \CC.size$\;
            \eIf {$\CC.cell[i] \geq value$}
            {
                \AtomDec{$\CC.cell[i]$, value}\;
            }{
                $r \gets value - \CC.cell[i]$\;
                \AtomSet{$\CC.cell[i]$, $0$}\;
                \Dec{\CC, r, seed, $attempt + 1$}\;
            }
        }
        \caption{Concurrent counter}\label{alg:CC}
    \end{algorithm}
